\documentclass[12pt]{article}
\usepackage{listings}
\usepackage[colorlinks=true,pagebackref,linkcolor=blue]{hyperref}
\textwidth=7in
\textheight=9.5in
\topmargin=-1in
\headheight=0in
\headsep=.5in
\hoffset  -.85in

\lstset{
basicstyle=\footnotesize\ttfamily,
language=bash,
upquote=true,
breakatwhitespace=true,
columns=fullflexible,
keepspaces,
%numbers=none,
tabsize=3,
frame=blrt,
framextopmargin=5pt,
showstringspaces=false,
extendedchars=true
}

\pagestyle{empty}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\begin{document}



\begin{center}
{\bf AMS 550.400 \quad Midterm Presentation Assignment \quad  Due Date:  {Wed,
    Oct 17}}\\
\vskip.2in
{\footnotesize Last Compiled on \today}
\end{center}

\setlength{\unitlength}{1in}

\begin{picture}(6,.1) 
\put(0,0) {\line(1,0){6.25}}         
\end{picture}

\renewcommand{\arraystretch}{2}


\begin{center}
\bf{General Turn-in Instruction} 
\end{center}
To complete this homework set, you are required to do the followings. 
Your work must be typed in \LaTeX\ using the course presentation template.  
The progression of your midterm presentation is to be
``recorded'' by making a git folder specifically for this midterm
presentation homework set. 
The burden of proof is on you, and if your git commit history
is sparse, then you may be liable for a penalty.  
A paper copy of the PDF output of your \LaTeX\ file is 
to be submitted to your instructor in class on the due date.
\emph{After} submitting the paper copy, but \emph{before} the end of
the due date, you will upload your work to your github by making a remote repository
specifically for the homework, and post the link to the repository 
at the designated \emph{Discussion} forum in Blackboard by making 
a thread just for you.  The repository name in your github should be
\texttt{550400.workstatement.final} and the discussion forum thread should
be named \texttt{YourFirstNameMiddleInitialLastName}, e.g.,
\texttt{BaracHObama} and \texttt{WillardMRommey}. 
You have till the end of the due date to finalize your github repository.  
However, any commit made after the class time of the due date will be 
inadmissible.  Finally, upload your video file to \emph{your}
Discussion Forum thread, i.e., \texttt{YourFirstNameMiddleInitialLastName}.  
\emph{Your attention to details in following this instruction will be 
critical, and if not followed exactly at the time of collection, the
homework set may be graded at $90\%$ of the full score}.

\vskip.25in

\begin{center}
{\bf  Midterm Presentation\footnote{Some of these materials are
    from \cite{RIPS2012}.} }
\end{center}

A major component of this course is training and practice in
giving good talks, presenting orderly information in a short
time. It is an art form requiring practice and discipline. You will
want to be good at giving a talk by the time of your midterm
presentation.  Public speaking is, for many, an intimidating experience at first, so
it helps to have an orderly process for getting used to it. Here are
some suggestions on how to prepare a presentation. 
The secret is repetition. The idea is to hold regular
practice sessions within your team, paying attention to timing and
structure. And don't worry about it if initially you mumble and
fumble. Practice makes perfect!

Your particular assignment in this homework set is to prepare a 20 min 
talk about the project that  you wrote in the work statement. This has two 
parts: 
\begin{itemize}
\item making beamer/LaTeX presentation slides,
\item making a presentation video of giving a talk.
\end{itemize}

What I meant by making a presentation video 
is that you should make a movie file in format such as 
\texttt{mpeg} or \texttt{avi} so that 
the screen shows the slide that you 
are currently explaning in the background.
You do not need to make it so that you actually 
appears in the movie but I do not prohit you from doing so. 

You should make your recording as good as possible,
and try multiple times before finalizing the recording. 
How would you make such a video recording? 
For OSX, QuickTime Player does make a 
simultaneous recording of voice and screen, and it 
comes with OSX by default. You can find it under 
the usual Applications folder.  
Unfortunately, for Windows, QuickTime Player does not 
come with the same functionalities as the OSX version. However, 
there are many  free softwares that will satisfy your needs. 
An example of such a software can be found in the following webpage
(\url{http://camstudio.org}).

The time requirement is strict in a sense that 
you should not go over 20 minutes. Making 
it exactly 20 minutes is hard. To give you a sense of  
what is being considered acceptable, 
I would say 18 or 19 minutes 
are okay if your presentation naturally breaks there,
but 15 minutes would be too short for any case. 
If you find yourself that you do not have enough 
materials to talk about beyond, say 15 minutes, 
then that probably means that you have not given your project a
serious consideration.

Roughly speaking, the contents of the talk should be a presentation
version of the work statement and any preliminary 
progress you have made in your project. A template for formal
presentations is shown next. Don't go overboard
in preparing colorfully dynamic and impressive graphics--except to the
extent that the graphics help directly to explain the technical
material and purpose of the project. 
\begin{itemize}
\item INTRODUCTION (5 minutes, approximate) (crystallized
  introduction, clarity for average listener)
\begin{itemize}
\item Title, sponsor identification, participants
\item Sponsor's business, relevance to problem area
\item Description/explanation of problem
\item List of deliverables
\end{itemize}
\item HEART OF TALK (10 minutes, approximate)
\begin{itemize}
\item Team's approach, in descriptive non-specialist language
\item Research accomplished -- discuss analysis/results -- oriented toward
specialists
\end{itemize}
\item CONCLUSION (5 minutes, approximate)
\begin{itemize}
\item Check against list of deliverables
\item Discuss work remaining to be done, negative results
\item Recommendations for future research
\end{itemize}
\end{itemize}



\begin{center}
{\bf Appendix}
\end{center}

It is important to understand how others view your presentation,
whether your points are clearly expressed and convey the essence of
your project adequately. There are many dimensions (or scales) on
which a talk can be judged. 

For the style guide for your presentation, please see 
Chapter 15 (Speaking about Multivariate Analysis) of \cite{WMA2005}.
In addition, the following list\footnote{This list
  is the same one in \cite{WMA2005} which itself is due to Prof.\  Robert Wolf of Harvey Mudd College.} suggests some dimensions that
can help you evaluate your own talk and guide you in making
suggestions to others.

\begin{itemize}
\item Dress:  Are presenters wearing suits or similar clothing of
  professional appearance? 

\item Introduction: Do we learn who the speaker and other team members are?
Do we understand who the client is and what its business is?

\item Problem Statement:  Do we understand the problem presented to
  the team and how it fits into the client’s business? Do we learn why
  the problem is important?

\item Objectives: Are the objectives of the clinic clear? Is what
  constitutes a solution clear? 

\item Constraints: Are the constraints on the clinic objective clear?
  Are there cost, quality, performance, accuracy, reliability,
  usability, or other constraints?

\item Approach: Do we understand the approach to be used in reaching
  the project objectives? Is the reason for the approach clear? Is the
  sequence of activities clear?

\item Alternatives: Has the team studied alternative approaches to
  reach a solution of the problem? Have all plausible alternatives
  been considered? How were the alternatives evaluated?

\item Evaluation: Have the criteria for ranking and evaluating
  solutions been explained? Is there a metric? Do the ranking criteria
  meet the objectives and constraints?

\item Budget: Is the budget for the project clear? Is it complete?
  Realistic? Achievable?

\item Schedule: Is there a detailed schedule of work, with milestones
  and personnel identified? Is the time line, grant chart, or pert
  chart useful for detailed planning and assessment of the team’s
  progress? Can it be modified to deal with delays?

\item Deliverables: What exactly will be the deliverables for the
  project to the client? 

\item Acknowledgements: Have the liaison, advisor,
  consultants, and staff been recognized for their efforts?

\item Questions: Have the team as a group responded adequately to the
  questions asked? Did they seem receptive to advice? Were the
  questions repeated for clarity?

\item Visuals: Were the slides clear, not cluttered, and attractive?
  Did they give adequate information?

\item Speaking: Did the students speak clearly and confidently in
  standard English? Was the talk well organized? Well paced? Was the
  logic clear? Were all the important points covered in adequate
  detail?

\end{itemize}

If your audience is satisfied on all these points, you have made an excellent presentation!

\bibliographystyle{plain}
\nocite{*}
\bibliography{biblioMP}

\end{document}
