\documentclass[12pt]{article}
\usepackage{listings}
\usepackage[colorlinks=true,pagebackref,linkcolor=blue]{hyperref}
\textwidth=7in
\textheight=9.5in
\topmargin=-1in
\headheight=0in
\headsep=.5in
\hoffset  -.85in

\lstset{
basicstyle=\footnotesize\ttfamily,
language=bash,
upquote=true,
breakatwhitespace=true,
columns=fullflexible,
keepspaces,
%numbers=none,
tabsize=3,
frame=blrt,
framextopmargin=5pt,
showstringspaces=false,
extendedchars=true
}

\pagestyle{empty}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\begin{document}



\begin{center}
{\bf AMS 550.400 \quad Team Formation  Assignment \quad  Due Date:  {Monday,  Oct 8}}\\
\vskip.2in
{\footnotesize Last Compiled on \today}
\end{center}

\setlength{\unitlength}{1in}

\begin{picture}(6,.1) 
\put(0,0) {\line(1,0){6.25}}         
\end{picture}

\renewcommand{\arraystretch}{2}

\begin{center}
{\bf  Team Formation Activites Groups}
\end{center}

The following list is only for the class activity only although 
some thoughts have been given for this particular choice.  
\begin{itemize}
\item  Shihong Li, Steven Su, Jing Huang, Hua Hua, Du Yu,
\item  Joyce Tan, Danni Tang, Yen Theng Tan, Yue Wu, Rong Fan,
\item  Jordan Mandel, Zhenhan Zhao,  Jonathan Ho, Yixuan Da, Du Yu  
\item Zichan Wang, Michael Weinberger, Shannon Cebron, Zhendan Zhu
\item Ahmed Aly, Tianyu Luo, Huinan Zhang, Xiaohan Yang
\end{itemize}
\vskip0.25in

\begin{center}
{\bf Getting to Know Your Class Activity Group}
\end{center}

Locate the group members and then do the following:
\begin{itemize}
\item Someone should volunteer to keep the meeting organized,
\item Get to know your groupmates' name and their favoriate
  non-academic activities,
\item Give an overview of your project idea with your teammates,
\item Discuss what you think the ``strength/advantage'' of your
  project,
\item Figure out if all of you can meet at a certain time if needed.
\end{itemize}
Appropriately, summarize your finings in the back of this paper.  
\vskip0.25in

\begin{center}
{\bf Deciding on Your Class Project Team}
\end{center}

By the end of today's lecture, you should decide on your course of
action.  You have three potential options: 
\begin{itemize}
\item Stick with your current group assignment,
\item Form a new team,
\item Be your own team.
\end{itemize}
Your instructor has the final say on your class project team and the
team project.  If you want  to go alone, then your project must be
approved by the instructor.  If your project is not approved, then you
must join another team in order to complete the course.  Write down
your decision in the back of this paper.  Once approved by your
instructor, \emph{each} of you should post your teams in \emph{your
  own thread} in the designated Blackboard forum. 
\bibliographystyle{plain}
%\nocite{*}
\bibliography{biblioMP}

\end{document}
